Simulataneous Robot Localization and \\Environment Mapping with \\Simulated Sensor Measurements

### 2018-05-03 paper.tex
meh

@@

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

@@

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

>>>>

The EKF SLAM algorithm was unsuccessful in accurately localizing the robot and landmarks. The 
algorithm was executed using sensor models for the Microsoft Kinect and gyro. Figures \ref{fig:1}-\ref{fig:3}
present the error between the actual and estimated pose of the robot. The estimated $x$ and $y$ positions of the 
robot did not converge to the actual positions, with errors ranging from $-1.5$ meters to $1$ meter. However, 
the estimated angular orientation of the robot closely matched the actual angular orientation with the 
difference staying within $0.2$ radians. This is likely due to the high accuracy of the gyroscope sensor. 
Figures \ref{fig:4}-\ref{fig:6} present the variances for the estimate pose of the robot. The figures clearly demonstrate 
the effects of the prediction and correction step on the variance. The variance for each pose value 
increases during the motion model update and then decreases in the correction step with the sensor 
model updates. This accounts for the sporadic appearance of the data. However, the average variance 
reduces over time and converges to a limit. Figure \ref{fig:7} shows the number of unique landmarks stored in the 
map built by the algorithm. Despite only three landmarks being present in the environment, the algorithm 
identified 254 landmarks, indicating significant errors in data association between new observations and 
previous observations.

@@

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{Description of Attached C++ Files}
\begin{itemize}
 \item \texttt{EKFSlammer.h} --- Defines all prediction step and correction step methods for the robot
 and obstacles, given all types of sensor inputs. 
 \item \texttt{EKFSlammer.cpp} --- Implements all the methods defined in \texttt{EKFSlammer.h}.
 \item \texttt{Robot.h} --- Defines and implements the conceptual robot and declares functions for 
  extracting (noisy) sensor measurements from the robot's defined sensors.
 \item \texttt{main.cpp} --- Creates instances of the \texttt{Robot} and the \texttt{EKFSlammer} and extracts data from
  their actual (\texttt{Robot}) results and their calculated (\texttt{EKFSlammer}) results.
 \item \texttt{Utils.h} --- Defines the \texttt{controlIn} struct, which is used to input a control to the \texttt{Robot}
  and \texttt{EKFSlammer} instances.
\end{itemize}

@@
